---
title: "Dev.Econ"
author: "Aziz"
date: '2022-07-15'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
```

Calling the libraries

```{r}
library(here)
library(haven)
library(dplyr)
library(tidyr)
library(plm)
library(fixest)
library(Hmisc)
library(modelsummary)
```

Showing the path to the data file

```{r cars}

here::i_am("model_replication.Rmd")
dir_data    <- here("../data")
dir_graph_data <- here("../graph")


```

Reading ethnic data and cleaning

```{r}
filename <- "ethnicinflow.dta"

ethnic <- read_dta(paste( dir_data, filename, collapse = " + ", sep = "/" )) %>%
  select(
    ethnicinflow, c(-"county_type", -"state")) %>%
  mutate(
    lag_ethnic1 = Lag(ethnicinflow))%>%
  filter(year %in% c(1994:2006))

```

Reading crime data and cleaning

First I am lagging and then slicing the period 1996 - 2006. That's why, even though counties get the lagged data for 1995 from another county in 2006, it will not create a problem of mixing data among counties. Because then I am trimming the necessary period interval from 1994 to 2006.

This rule applies to all the formulas where lag is used

```{r}
filename <- "crime.dta"

crime<- read_dta(paste( dir_data, filename, collapse = " + ", sep = "/" ))%>%
  arrange(id, year)%>%
  select(2,3,5,6,29,25)%>%
  mutate(
    change_clear_up <- (dr_offense - Lag(dr_offense,1))/100,
    change_crime <- offense_total - Lag(offense_total,1))%>%
  filter(year %in% c(1996:2005))


colnames(crime)[5:8] <- c("reported", "clear_up", "change_clear_up", "change_crime")

```

Reading population data and cleaning

```{r}
filename <- "population.dta"

population <- read_dta(paste( dir_data, filename, collapse = " + ", sep = "/" ))%>%
  select(c(-"county_type")) %>%
  arrange(id, year) %>%
  mutate(
         foreign_share = poptotalforeign / poptotal,
         lag_pop1 = Lag(poptotal),
         lag_pop2 = Lag(poptotal,2),
         change_shareforeigners= foreign_share - Lag(foreign_share),
         change_logpop=log(poptotal)-log(lag_pop1)) %>%
  filter(year %in% c(1996:2006))

```

Reading agestructure data and cleaning

```{r}
filename <- "agestructure.dta"

agestructure <- read_dta(paste( dir_data, filename, collapse = " + ", sep = "/" ))%>%
  arrange(id, year)%>%
  mutate(
    pop15_39 = pop15_17M + pop18_19M + pop20_24M + pop25_29M + pop30_34M + pop35_39M,
    lag_pop15_39 = Lag(pop15_39),
    pop15_64 = pop15_17M + pop18_19M + pop20_24M + pop25_29M + pop30_34M + pop35_39M + 
                          pop40_44M + pop45_49M + pop50_54M + pop55_59M + pop60_64M,
    lag_pop15_64 = Lag(pop15_64)) %>%
  select(1,2,57,58,59,60)

```

Reading GDP data and cleaning

Below, all formulas in the form of change_x = x - lag(x) captures the change of x compared to the previous year

```{r}
filename <- "gdp.dta"

gdp <- read_dta(paste( dir_data, filename, collapse = " + ", sep = "/" )) %>%
  arrange(id, year) %>%
  mutate(
    change_loggdp_percap = log(gdpcapita) - Lag(log(gdpcapita))) %>%
  filter(year %in% c(1996:2006)) %>%
  select(c("id", "year", "change_loggdp_percap"))

```

Reading unemployment data and cleaning

```{r}
filename <- "unemployment.dta"

unemployment <- read_dta(paste( dir_data, filename, collapse = " + ", sep = "/" )) %>% 
  arrange(id, year) %>% 
  mutate(
    change_unemploy = alq_dep_A - Lag(alq_dep_A)) %>%
  select("id", "year", "change_unemploy") %>%
  filter(year %in% c(1996:2006))
  
```

creating main variables: y and x

```{r}
main_var <- left_join(
  crime, 
  select(population, -c("state", "county")), by=c("id", "year")) %>%
  mutate(y = change_crime / lag_pop1)%>%        
                                      # y is the dependent variable in question
  left_join(select(ethnic, -c("county")), by=c("id", "year")) %>%
  mutate(inflowrate = lag_ethnic1 / lag_pop2) 
                                      # inflowrate is the main x variable in question

```

Compiling other data in a data frame, X_data

```{r}
X_data <- left_join(
  population, agestructure, by=c("id", "year")) %>%
  mutate(
    change_shareyoungM = (pop15_39 / poptotal) - (lag_pop15_39 / lag_pop1),
    change_shareM = (pop15_64 / poptotal) - (lag_pop15_64 / lag_pop1)) %>%
  left_join(
    gdp, by=c("id", "year"))%>%
  left_join(
    unemployment, by=c("id", "year"))%>%
  filter(year %in% c(1996:2006))

```

final data set

```{r}
# selecting necessary columns from X_data to merge easily
temp <- select(X_data, "id", "year", "change_logpop", "change_loggdp_percap", 
            "change_unemploy", "change_shareforeigners", "change_shareyoungM", "change_shareM")

final_data <-  select(main_var, "id", "year", "state", "county", "y", "inflowrate", "change_clear_up")%>%
  left_join(temp, by= c("id", "year"))%>%
  as.data.frame(final_data)

```

Running fixed effect regression models

```{r}

flm_model <- feols(y ~ inflowrate + change_logpop + change_loggdp_percap +
                 change_unemploy + change_shareforeigners +
                 change_shareyoungM + change_clear_up | state ^ year + county, vcov = (cluster = "twoway"), 
                 data = drop_na(final_data))


flm_model2 <- feols(y ~ inflowrate + change_logpop + change_loggdp_percap +
                 change_unemploy + change_shareforeigners +
                 change_shareyoungM + change_clear_up | state + year + county,  cluster = c("state", "id", "year"),
                 data = drop_na(final_data))


flm_model3 <- feols(y ~ inflowrate + change_logpop + change_loggdp_percap +
                 change_unemploy + change_shareforeigners +
                 change_shareM + change_clear_up | state ^ year + county, vcov = (cluster = "twoway"), 
                 data = drop_na(final_data))



cm <- c('inflowrate' = "Ethnic German inflow rate (t-1)",
        'change_logpop' = "Change in Log pop (t)",
        "change_loggdp_percap" = "Change in Log GDP per capita (t)",
        "change_unemploy" = "Change in unemployment rate (t)",
        "change_shareforeigners" = "Change in foreigners share (t)",
        "change_shareyoungM" = "Change in young male's share (aged 15-39) (t)",
        "change_shareM" = "Change in male's share (aged 15-64) (t)",
        "change_clear_up" = "Change in clear-up rate (t)")


models <- list("Model 1"=flm_model,
               "Model 2 (fixed effects)"=flm_model2,
               "Model 3 (age15_64)" = flm_model3)


modelsummary(models, stars = T,  gof_omit = "AIC|BIC|RMSE", coef_map = cm, title = "Table 1")

```

